---
title: "p8105_hw1_yw3438"
output: github_document
author: "Yuning Wang"
---

# Problem 1

## First Code Chunk
Here's the first code chunk for problem 1:

```{r message=FALSE}
library(tidyverse)

problem1_df = tibble(
  ran_sample = rnorm(8),
  gr_th_0_logical = ran_sample > 0,
  vec_character = c("This", "is", "the", "answer", "of", "problem", "one", "here"),
  vec_factor = factor(c("white", "black", "black", "red", "white", "red", "black", "white"), levels = c("white", "black", "red") )
)

lapply(problem1_df, mean)
##The clss of vec_character is character and the class of vec_factor is fact.##
##The mean of vec_character and vec_factor cannot be calculated, because they are neither numerical nor logical vectors##
```

## Second Code Chunk
Here's the second code chunk for problem 1:
```{r}
##convert the logical vector to numeric, and multiply the random sample by the result##
gr_th_0_num = as.numeric(problem1_df$gr_th_0_logical)
prod(gr_th_0_num)

##convert the logical vector to a factor, and multiply the random sample by the result##
gr_th_0_fac = as.factor(problem1_df$gr_th_0_logical)
#gr_th_0_fac_pro = prod(gr_th_0_fac)
#the random sample cannot be mutiplied as it's factor. I have to put it into a comment because the whole Rmd will break down if it's in the code.

##convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result##
gr_th_0_fac_num = as.numeric(as.factor(problem1_df$gr_th_0_logical))
prod(gr_th_0_fac_num)
```



# Problem 2

```{r}
problem2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_logic2 = x + y > 1,
  vec_num2 = as.numeric(vec_logic2),
  vec_fac2 = as.factor(vec_logic2)
)
```
The size of this dataset can be described by its columns and rows. The number of the columns is `r ncol(problem2_df)` and the number of the rows of the dataset is `r nrow(problem2_df)`.

The mean of x is `r mean(problem2_df$x)`, the median of x is `r median(problem2_df$x)` and the standard deviation of x is `r sd(problem2_df$x)`.

The proportion of cases for which x + y > 1 is `r sum(problem2_df$vec_num2)/length(problem2_df$vec_num2)`

## The Scatterplot of x and y

### Color points using logical variables
```{r}
ggplot(problem2_df, aes(x = x, y = y)) + geom_point(aes(color = vec_logic2))
```

### Color points using the numeric variables
```{r}
ggplot(problem2_df, aes(x = x, y = y)) + geom_point(aes(color = vec_num2))
```

### Color points using the factor variables
```{r}
ggplot(problem2_df, aes(x = x, y = y)) + geom_point(aes(color = vec_fac2))
```

```{r}
##save the first plot##
logic_color_plot = ggplot(problem2_df, aes(x = x, y = y)) + geom_point(aes(color = vec_logic2))
ggsave("logic_color_plot.pdf", logic_color_plot, width = 8, height = 5)
```
